LOINC2HPO_EPIC AND SCC

### 2022-04-21 code/r/MSDW_HPO_Phenotype_Analysis.Rmd
reorg project structure

>>>>

### Visualize patient phenotypic journey
```{r}
get_patient_lab_phenotype_journeys <- function(medical_record_numbers, force_rerun=FALSE, cache_dir=CACHE_DIR) {
  df_path = glue('{cache_dir}/patient_lab_phenotype_journey.csv')

  mrns_str <- str_c("'", medical_record_numbers, "'", collapse = ',')

  if (force_rerun | !file.exists(df_path)){
    df <- dbGetQuery(dsca, glue("
            with patient_lab_results as (
            	select *, date_part(year, lab_date) as lab_year
            	from hai_az_prod.scc_and_epic_lab_after_loinc2hpo_2020july saelalhj 
            	where medical_record_number in ({mrns_str}) and hpotermid is not null 
            ),
            annual_phenotypes as (
            	select medical_record_number , lab_year, isnegated , hpotermid , count(*) as n 
            	from patient_lab_results 
            	group by medical_record_number , lab_year, isnegated , hpotermid
            ),
            annual_phenotypes_annotated as (
            	select *
            	from annual_phenotypes p
            	left join hai_az_prod.hpo h on p.hpotermid  = h.termid  
            	order by medical_record_number , lab_year, isnegated , hpotermid )
            select medical_record_number , lab_year, isnegated , hpotermid , n, label
            from annual_phenotypes_annotated
            order by medical_record_number , lab_year, isnegated , n desc, hpotermid
            ;
            "))

patient_lab_phenotype_journeys <- get_patient_lab_phenotype_journeys(medical_record_numbers = c('7611233'), force_rerun = FORCE_RERUN)
```

```{r}
patient_lab_phenotype_journeys_formated <- patient_lab_phenotype_journeys %>% 
  filter(medical_record_number == '7611233') %>% 
  select(-medical_record_number) %>% 
  group_by(lab_year, isnegated) %>% 
  slice_head(n = 5) %>% 
  mutate(display = glue('{hpotermid} {label} ({n} times)')) %>% 
  summarise(display = str_c(display, collapse = '\n'), .groups = 'drop')
write.csv(patient_lab_phenotype_journeys_formated, file = glue('{CACHE_DIR}/patient_lab_phenotype_journey_formatted.csv'))
```
